---
title: "LDA parameters tuning"
author: "Carlijn Diederiks"
date: "2023-06-15"
output: html_document
---

Make sure the preprocessing file has run first, before running this code. 

```{r}
#install.packages("ldatuning")
#install.packages("topicmodels")
#install.packages("topicdoc")
library(ldatuning)
library(topicmodels)
library(topicdoc)

#set a seed to reproduce the results
set.seed(920)
```

## Finding the optimal number of topics K 

We use the lda tuning function for optimalization of the topics K.

```{r}
#Takes some time to run

result <- FindTopicsNumber(
  dtm,
  topics = c(1:20 * 5, 120, 140, 160, 180),
  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010"),
  method = "Gibbs",
  control = list(seed = 920),
  mc.cores = 6L,
  verbose = TRUE
)
```

The result is plotted.

```{r}
plot <- FindTopicsNumber_plot(result)
```

## Tuning the alpha and beta 

Tuning the optimal alpha and beta for the LDA topic model by comparing the coherence scores. The coherence scores are measured ten times and the mean is presented (because each model is different). 

The optimal number K as optimized above, has to be set here first. 

```{r}
set.seed(920)

# Assign the optimal number of topics
topic.count <- 25

# Define the range of values for alpha and beta
alpha_values <- c(0.01, 0.05, 0.1, 0.5, 2, 5)
beta_values <- c(0.01, 0.05, 0.1, 0.5, 5)

# Create an empty data frame to store the results
results <- data.frame(alpha = numeric(), beta = numeric(), mean_coherence = numeric())

# Perform the grid search
for (alpha in alpha_values) {
  for (beta in beta_values) {
    # Create a vector to store the coherence scores for each iteration
    coherence_scores <- numeric()
    
    # Run the LDA model and coherence calculation 10 times
    for (i in 1:10) {
      # Build the LDA model
      lda.model <- LDA(dtm, topic.count, method = "Gibbs", alpha = alpha, eta = beta)
      
      # Calculate the topic coherence with the top 20 tokens
      diag <- topic_diagnostics(lda.model, dtm, top_n_tokens = 20)
      
      # Calculate the mean topic coherence
      mean_coherence <- mean(diag$topic_coherence)
      
      # Add the mean coherence score to the coherence_scores vector
      coherence_scores <- c(coherence_scores, mean_coherence)
    }
    
    # Calculate the average of the coherence scores
    mean_coherence_avg <- mean(coherence_scores)
    
    # Create a data frame with the current results
    current_result <- data.frame(alpha = alpha, beta = beta, mean_coherence = mean_coherence_avg)
    
    # Append the current result to the overall results data frame
    results <- rbind(results, current_result)
  }
}

# Print the results
print(results)

```

We save the results of the alpha en beta tuning as a csv file. 

```{r}
write.csv(results, file = "LDA_tuning.csv", row.names = FALSE)
```

